Quantum Hoare Type Theory

### 2020-05-08 ms-paper/ms-paper.tex
Minor updates
Fix minor type, add some todos

\renewcommand*\contentsname{Table of Contents}
\tableofcontents

@@

\paragraph{Computations} The computations are the usual monadic return and (three) bind operations as in HTT.

@@

We can now show some typing rules:

@@

\todo{The type should be \type{Bool} $\otimes$ \type{Bool}}
\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}  -- a,b \in {true, false}
         = do qa <= mkQbit false;
              applyU (H qa);
              qb <= mkQbit false;
              applyU (ifQ qa (X qb));
              (measQbit qa, measQbit qb)
\end{lstlisting}

@@

\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}
              -- P0: emp
         = do qa <= mkQbit false;
              -- P1: P0 \o (qa |-> state(false))
              applyU (H qa);
              -- P2: P1 \o (qa |-> state({(0.5, false), (0.5, true)}))
              qb <= mkQbit false;
              -- P3: P2 \o (qa |-> state(false))
              applyU (ifQ qa (X qb));
              -- P4: P3 \o ((qa, qb) |-> state({(0.5, (false, false),
              --                              (0.5, (true, true))}))
                (measQbit qa, measQbit qb)
              -- P5: P4 \o ((qa |-> -) -o emp) \o ((qb |-> -) -o emp)
\end{lstlisting}
Finally, the \texttt{consq} rule should ensure that the assertion P5 can lead to the specified postcondition in the type of the program.

@@

\subsection{Bell pair}
\todo{The type should be \type{Qbit} $\otimes$ \type{Qbit}}
\begin{lstlisting}[language=QHaskell]
bell : {emp} (a, b) : (Qbit, Qbit) {Id(a, b) /\ a \in {|0\>, |1\>}}
     = do qa <- qplus;
          qb <- share qa;
          return (qa, qb)
\end{lstlisting}

>>>>

\tableofcontents

@@

\paragraph{Computations} The computations are the usual monadic return and (three) bind operations as in HTT. \todo{TODO: $\Leftarrow$ is currently overloaded with notation for type checking}

@@

We can now state the typing rules:

@@

\todo{TODO: The type should be \type{Bool} $\otimes$ \type{Bool}}
\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}  -- a,b \in {true, false}
         = do qa <= mkQbit false;
              applyU (H qa);
              qb <= mkQbit false;
              applyU (ifQ qa (X qb));
              (measQbit qa, measQbit qb)
\end{lstlisting}

@@

\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}
              -- P0: emp
         = do qa <= mkQbit false;
              -- P1: P0 \o (qa |-> state(false))
              applyU (H qa);
              -- P2: P1 \o (qa |-> state({(0.5, false), (0.5, true)}))
              qb <= mkQbit false;
              -- P3: P2 \o (qb |-> state(false))
              applyU (ifQ qa (X qb));
              -- P4: P3 \o ((qa, qb) |-> state({(0.5, (false, false),
              --                              (0.5, (true, true))}))
                (measQbit qa, measQbit qb)
              -- P5: P4 \o ((qa |-> -) -o emp) \o ((qb |-> -) -o emp)
\end{lstlisting}
Finally, the \texttt{consq} rule should ensure that the assertion P5 can lead to the specified postcondition in the type of the program.

@@

\subsection{Bell pair}
\todo{TODO: The type should be \type{Qbit} $\otimes$ \type{Qbit}}
\begin{lstlisting}[language=QHaskell]
bell : {emp} (a, b) : (Qbit, Qbit) {Id(a, b) /\ a \in {|0\>, |1\>}}
     = do qa <- qplus;
          qb <- share qa;
          return (qa, qb)
\end{lstlisting}
